Compositional Certified Resource Bounds

### 2014-07-03 paper/main.tex
minor

\begin{figure*}
\centering
\begin{tabular}{c|c|c|c}
%
\begin{lstlisting}
while (y > x) {
  x++; tick(1) }
while (x > 2) {
  x -= 3; tick(1) }
\end{lstlisting}
&
\begin{lstlisting}
while (i > 100)
  i--;
i += k+50;
while (i >= 0)
  i--;
\end{lstlisting}
&
\begin{lstlisting}
while (x > 0) {
  x--;
  t=x, x=y, y=t;
}
\end{lstlisting}
&
\begin{lstlisting}
assert(y >= 0);
while (x>y) {
  x -= y+1;
  for (z=y; z > 0; z--)
    /* skip */;
}
\end{lstlisting}
\\
%
\hline
t08a (slightly modified t08) & t19 & t30 & t15
%
\end{tabular}
\caption{
  Comparison of the bounds given by different tools on
  linear examples.
}
\label{fig:compar}
\end{figure*}

\begin{figure}
\includegraphics[width=\linewidth]{fig/bound3d}
\caption{The automatically derived bound $1.33|[x,y]| + 0.33 |[0,x]|$
  (blue lines) and the measured runtime cost (red crosses) for example
  \emph{t8a}. For $x\ge 0$ the derived bound is tight.}
\label{fig:3d}
\end{figure}

>>>>

\begin{figure*}
\centering
\begin{tabular}{t|c|c|c|c}
%
&
\begin{lstlisting}
while (y > x) {
  x++; tick(1) }
while (x > 2) {
  x -= 3; tick(1) }
\end{lstlisting}
&
\begin{lstlisting}
while (i > 100)
  i--;
i += k+50;
while (i >= 0)
  i--;
\end{lstlisting}
&
\begin{lstlisting}
while (x > 0) {
  x--;
  t=x, x=y, y=t;
}
\end{lstlisting}
&
\begin{lstlisting}
assert(y >= 0);
while (x>y) {
  x -= y+1;
  for (z=y; z > 0; z--)
    /* skip */;
}
\end{lstlisting}
\\
%
\hline
& t08a (slightly modified t08) & t19 & t30 & t15
%
\\
\hline
LOOPUS \\
Rank \\
AAA
\end{tabular}
\caption{ Comparison of resource bounds derived by different tools on
  several examples with linear bounds.  AAA stands for our automatic
  amortized analysis for Clight.  The output of Rank has been manually
  simplified to fit the table.  }
\label{fig:compar}
\end{figure*}

\begin{figure}
\includegraphics[width=\linewidth]{fig/bound3d}
\caption{The automatically derived bound $1.33|[x,y]| + 0.33 |[0,x]|$
  (blue lines) and the measured runtime cost (red crosses) for example
  \emph{t08a}. For $x\ge 0$ the derived bound is tight.}
\label{fig:3d}
\end{figure}
